---
title: "OnBaseU Movement Programming"
author: "Brock Hammit"
date: "10/8/2020"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(tinytex)
library(prettydoc)
```

```{r, echo=FALSE}

### OnBaseU Screen###############################

##### 1 = Red(Fail) ###########################
##### 2 = Yellow(semi Pass) ###################
##### 3 = Green(Pass) #########################


pelv.t <- 2
pelv.r <- 3
toe.t <- 3
hip.45 <- 2
seated.t.rot <- 3
lat.step <- 3
wide.sq <- 3
ank.rock <- 3
shld.46 <- 1
sep.test <-3
hold.ang <- 3
hitch.test <- 3


 


























































 #### Rotation Tests########
  

 Rot.Test.Pr <-  case_when(
   toe.t == 2 & hip.45 == 2 ~ " * **Toe Tap Exercises**- Hip Drops, Starfish Pattern, x 1-2 a Week & **Hip 45 Exercises**- Figure 4 Horizontal Bridge, Hip Drops, Starfish Pattern,  1-2 x a week",
    toe.t + hip.45 <=3  ~ " * Toe Tap Exercises- Hip Drops, Starfish Pattern, x 1-2 a Week & Hip 45 Exercises- Figure 4 Horizontal Bridge, Hip Drops, Starfish Pattern,  4-5 x a week",
    toe.t ==  1 ~ '* Toe Tap Exercises- Hip Drops, Starfish Pattern, Hip Flexor Stretch with Side Bend, 4-5 x a week',
  toe.t == 2 ~ '* **Toe Tap Exercises**- Hip Drops, Starfish Pattern, 1-2 x a week',
  hip.45 == 1 ~ '* **Hip 45 Exercises**- Figure 4 Horizontal Bridge, Hip Drops, Starfish Pattern, 4-5 x a week',
  hip.45 == 2 ~ '* **Hip 45 Exercises**- Figure 4 Horizontal Bridge, Hip Drops, Starfish Pattern, 1-2 x a week',
  TRUE ~ "" 
  )
  
seated.t.rot.pr <- case_when(
  seated.t.rot == 1 ~ "* **Seated T-Spine Rotation**- Reachbacks IR, Reachbacks ER, Seated Torso turns with Side Bend & Cervical Flexion 4-5 times a week",
  seated.t.rot == 2 ~ "* **Seated T-Spine Rotation**- Cervical Flexion 1-2 times a week",
  TRUE ~ "" )
  
  #### Core Control Tests#######
  
  c.conttol.pr <- case_when( pelv.t == 2 & pelv.r == 2 ~ "* **Pelvic Tilt Exercises**- Cat Dogs, Croc Breaths & Pelvic Rotation Exercises- Bretzel, Reachbacks IR, Reachbacks ER, Seated Torso turns with Side Bend x 1-2 a week",
                            pelv.t + pelv.r <= 3 ~ "*  **Pelvic Tilt Exercises**- Cat Dogs, Croc Breaths, x 1-2 a week & Pelvic Rotation Exercises- Bretzel, Reachbacks IR, Reachbacks ER, Seated Torso turns with Side Bend x 1-2 a week",
    pelv.t == 1 ~'**Pelvic Tilt Exercises**-Cat Dogs, Croc Breaths, x 4-5 a week',
                            pelv.t == 2 ~ ('* **Pelvic Tilt Exercises**- Cat Dogs, Croc Breaths, x 1-2 a week'),
                             pelv.r == 1 ~ '* **Pelvic Rotation Exercises**- Bretzel, Reachbacks IR, Reachbacks ER, Seated Torso Turns with Side Bend 5 x a week',
                            pelv.r == 2 ~ '* **Pelvic Rotation Exercises**- Bretzel, Reachbacks IR, Reachbacks ER, Seated Torso Turns with Side Bend 1-2 x a week',
    TRUE ~ "" )
  
  
  ######### Posture Control Tests##############
 
           lat.step.pr <- case_when(lat.step == 1 ~ '* **Lateral Step Exercises**- Ball Press Overhead, Lateral Hinge SL, SL stance, eyes open, Torso Turns SL x 4-5 a week',
            lat.step == 2 ~ '* **Lateral Step Exercises**-Ball Press Overhead, Lateral Hinge SL, SL stance, eyes open, Torso Turns SL x 1-2 a week',
            TRUE ~ "" )
           
 p.control.pr <- case_when( wide.sq == 2 &  ank.rock == 2 ~ "* Posture Control Hybrid 5 Day Temp",
                            wide.sq + ank.rock <=3 ~ "* **Wide Squat Exercises**- Dumbbell Assisted Deep Squat, Get Close to Ball, Half Kneeling Calf Stretch x 1-2 a week & **Ankle Rock Exercises**- Half Kneeling Calf Stretch, Bent Leg Calf Stretch 1-2 x a week ",
 wide.sq == 1 ~ '* **Wide Squat Exercises**- Dumbbell Assisted Deep Squat, Get Close to Ball, Half Kneeling Calf Stretch 4-5 x a week ', 
            wide.sq == 2 ~'* **Wide Squat Exercises**- Dumbbell Assisted Deep Squat, Get Close to Ball, Half Kneeling Calf Stretch 1-2 x a week',
            ank.rock == 1 ~ '* **Ankle Rock Exercises**- Half Kneeling Calf Stretch, Bent Leg Calf Stretch x 4-5 a week',
            ank.rock == 2 ~'* **Ankle Rock Exercises**- Half Kneeling Calf Stretch, Bent Leg Calf Stretch x 1-2 a week',
 TRUE ~ "" )
  
  
  ##### Live and Independent Hands #####
  
shld.46.pr <- case_when(shld.46 == 1 ~ '* **Shoulder 46 Exercises**- Box Press, Palm-Forearm Presses x 4-5 a week',
        shld.46 == 2 ~  '* **Shoulder 46 Exercises**- Box Press, Palm-Forearm Presses x 1-2 a week')

      sep.test.pr<- case_when(sep.test == 1 ~ '* **Seperation Test Exercises**- Push-Pulls, Reach Roll Lifts x 4-5 a week',
        sep.test == 2 ~'* **Seperation Test Exercises**-Push-Pulls, Reach Roll Lifts x 1-2 a week',
        TRUE ~ "" )
        
      hold.ang.pr <- case_when(hold.ang == 1 ~ '* **Holding Angle Exercises**- Wrist Ext, Wrist Flex, KB Upholds X 4-5 a week',
        hold.ang == 2 ~ '* **Holding Angle Exercises**- Wrist Extensions, Wrist Flexions, KB Upholds X 1-2 a week')
       
     hitch.test.pr <-  case_when( hitch.test == 1 ~ '* **Hitch Hiker Exercises**- Hammer Drill, DB Turn & Holds X 4-5 a week' ,
        hitch.test == 2  ~ '* **Hitch Hiker Exercises**- Hammer Drill, DB Turn & Holds X 1-2 a week',
        TRUE ~ "" )
```
  
 
# Athlete Name: **Terry Hoitz**


##                Weekly Movement Programming

### `r if(toe.t + hip.45 + seated.t.rot < 9) {" Rotational Movement"}`
`r if(toe.t + hip.45 + seated.t.rot < 9) {"For the athletes rotational movement they should be doing:"}`


`r   if(toe.t + hip.45 < 6){Rot.Test.Pr}`
`r if(seated.t.rot < 3) { seated.t.rot.pr}`

### `r if(pelv.r + pelv.t < 6) {"Core Control Movement"}`
`r if(pelv.r + pelv.t < 6) {"For the athletes core control movement they should be doing:"}` 

`r  if(pelv.r + pelv.t < 6){ c.conttol.pr}`


### `r if(lat.step + ank.rock + wide.sq < 9){"Posture Control Movement"}`
`r if(lat.step + ank.rock + wide.sq < 9){"For the athletes posture control movement they should be doing:"}`

`r if(ank.rock + wide.sq < 6){p.control.pr}`
`r if(lat.step < 3){lat.step.pr}`

### `r if(shld.46 + sep.test + hold.ang + hitch.test < 12){"Live & Independent Hands Movement"}`
`r if(shld.46 + sep.test + hold.ang + hitch.test < 12){"For the athletes live and independent hands movement they should be doing:"}`

`r  if(shld.46 < 3){shld.46.pr}`
`r  if(sep.test < 3){sep.test.pr}` 
`r  if(hold.ang <3){hold.ang.pr}`
`r  if(hitch.test < 3){hitch.test.pr}`



