---
title: <center> <h1>Hitter Report</h1> </center> 
author: "Brock Hammit"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



### Athlete Name:**Rhett Hendricks**


### Assesment Period: Oct 01, 2020 to Oct 14, 2020

***

```{r, echo=FALSE, include=FALSE}

# Player Report

library(dplyr)
library(ggplot2)
library(kableExtra)
library(prettydoc)
library(ggthemes)
library(mgcv)
library(tidyverse)
library(patchwork)

```
```{r, echo=FALSE}
### Player Name
player <- "Rhett Hendricks"
```
```{r, echo=FALSE}

ht.all <- read.csv('ht.all.10.17.csv')
ht.all$n.date <- strptime(ht.all$Date,"%m/%d/%y")


```
```{r, echo=FALSE}


r21.blast <- read.csv('r21.blast.all.csv')

r21.blast$n.date <- strptime(r21.blast$Date,"%d-%b-%y")

```





# **Batted Balls**

&nbsp;

 <center> <h3>Summary Statistics </h3> </center> 




```{r, echo=FALSE}

###Hittrax####


ht.bip <- filter(ht.all, Velo >= .1,)

senior.ht <-  ht.bip %>%
  filter(User %in% c ("Avery Grant","Caden Davis","Rhett Hendricks","Jeremy Rader"))

senior.hh <- senior.ht %>% 
  filter(Velo > 85)

######MUST INPUT USERS NAME######

player.ht <- filter(ht.all, n.date >= "2020-10-01" & n.date <= "2020-10-17", User == "Rhett Hendricks")
player.ht.bip <- filter(ht.all, n.date >= "2020-10-01" & n.date <= "2020-10-17", Velo >= .1,  User == "Rhett Hendricks")

# EV
p.avg.ev <- mean(player.ht.bip$Velo)
p.avg.ev <- round(p.avg.ev,digits  = 1)

p.max.ev <- max(player.ht.bip$Velo)
p.max.ev <- round(p.max.ev, digits = 1)
#AVG LA
p.avg.la <- mean(player.ht.bip$LA)
p.avg.la <- round(p.avg.la, digits = 1)

p.sd.LA <- sd(player.ht.bip$LA)
p.sd.LA <- round(p.sd.LA, digits = 1)
#Top 8 AVG EV and LA
 
p.t8 <- player.ht.bip %>% slice_max(Velo, n = 8)

p.t8.avg.la <- mean(p.t8$LA)
p.t8.avg.la <- round(p.t8.avg.la, digits = 1)

p.t8.avg.ev <- mean(p.t8$Velo)
p.t8.avg.ev <- round(p.t8.avg.ev, digits = 1)
#Athlete EV list

Names <- c(player,"Major League Avg")
Average.Exit.Velocity <- c(p.avg.ev, 89)
Max.Exit.Velocity <- c(p.max.ev, 111)

# Athlete LA List
Average.Launch.Angle <- c(p.avg.la, 12)
Standard.Dev.Launch.Angle <- c(p.sd.LA, 26.7)

bb.df <- data.frame(Names, Average.Exit.Velocity,Max.Exit.Velocity)
```


```{r, echo=FALSE, out.width="50%"}

bb.df %>%
  kbl() %>%
  kable_paper("hover")
```

* All things related back to MLB level. If players are to succeed in becoming a professional players, they must be able to hit balls as hard as major leaguers.

&nbsp;

```{r, echo=FALSE, out.width="50%", include=FALSE}

#Velo

s.ht.velo.df <- senior.ht %>%
  group_by(User) %>% 
  summarise_at(vars(Velo ), list(mean))

s.ht.velo.df <- s.ht.velo.df %>%
  mutate(AVG_EV = s.ht.velo.df$Velo)

s.hh.velo.df <- senior.hh %>%
  group_by(User) %>% 
  summarise_at(vars(Velo ), list(mean))

s.hh.velo.df <- s.hh.velo.df %>%
  mutate(AVG_EV_85 = s.hh.velo.df$Velo)

total.velo.df <- merge(s.ht.velo.df, s.hh.velo.df, by= "User")


total.velo.df <- select(total.velo.df, -c(Velo.x, Velo.y))
#LA

s.ht.la.df <- senior.ht %>%
  group_by(User) %>% 
  summarise_at(vars( LA), list(mean,sd)) 


s.ht.la.df <-  s.ht.la.df  %>%
  mutate(Avg_LA = s.ht.la.df$fn1) %>%
  mutate(SD_LA = s.ht.la.df$fn2)


s.ht.la.df <- select(s.ht.la.df, -c(fn1, fn2))

#LA85

s.hh.la.df <- senior.hh %>%
  group_by(User) %>% 
  summarise_at(vars( LA), list(mean,sd)) 


s.total.bb <-  s.ht.la.df  %>%
  mutate(Avg_LA_85 = s.hh.la.df$fn1) %>%
  mutate(SD_LA_85 = s.hh.la.df$fn2)


LA.EV.df <- merge(total.velo.df,s.total.bb, by="User")



```

<center> <h3>Exit velocity & Launch Angle </h3> </center> 


```{r, echo=FALSE,out.width="50%"}
 

LA.EV.df %>% 
  kbl(digits = 1) %>%
  kable_paper("hover")

```
* One of the major things to look for here is discrepancies between average launch angle, and average launch angle of well hit balls. Hitters must optimize their well struck balls, and must hit them at optimal angles to do so. 

* Standard deviation of Launch Angle has been found to be a good proxy of the hit tool. As important as it is to hit balls at good angles, hitting them there consistently is equally important. A smaller standard  deviation of launch angle is what we're wanting to develop. 

***

&nbsp;

```{r, echo=FALSE,  message=FALSE, include=FALSE}

###Read in CSV file and rename columns ####


HT = read.csv("ht.all.10.17.csv") 

###configure strike zone for grid####
range(HT$POI.X)
range(HT$POI.Y)

#gam_function
ls_gam_fit <- function(d){
  gam(Velo ~ s(POI.X, POI.Y),
      data=d)
}

#tile_plot
tile_plot_m <- function(fit){
  df_p <- expand.grid(POI.X = seq(-20, 20, length=50),
                      POI.Y = seq(15, 50, length=50))
  #get heatmaps by area
  df_p$lp <- predict(fit,df_p)
  
  #set strike zone according to HitTrax coordinates
  topKzone <- 41.7
  botKzone <- 22.3
  inKzone <- -8.5
  outKzone <- 8.5
  kZone <- data.frame(
    x=c(inKzone, inKzone, outKzone, outKzone, inKzone),
    y=c(botKzone, topKzone, topKzone, botKzone, botKzone)
  )
  ##tile ggplot and add kZone path               
  ggplot(df_p) +
    geom_tile(data=df_p,
              aes(x=POI.X, y=POI.Y,
                  fill= lp))   +
    scale_fill_distiller(palette = "Spectral")+
    geom_path(aes(x, y), data=kZone,
              lwd=1, col="red") +
    xlim(-15,15) +
    ylim(15,60)  +
    coord_fixed() +
    labs(fill = "Velo", breaks = c (50,110)) 
}

#setup in play to remove NA or 0 EV obs
setup_inplay <- function(data) {
  data %>% filter(Velo > 0)
}

ev_plot <- function(data, title = "Exit Velo"){
  data %>%
    setup_inplay() %>%
    ls_gam_fit() %>%
    tile_plot_m() +
    ggtitle(title) 
}

```

<center> <h3>Heat Map </h3> </center> 


```{r, echo=FALSE, warning=FALSE, fig.align='center'}

ev_plot(data = HT, title = "Rhett Hendricks")  +
  labs( x = "Plate Width(Catcher View)")  + 
  theme(plot.title = element_text(hjust = 0.5))
```

***



```{r, echo=FALSE,out.width="50%", warning=FALSE}
la.sd.pl <- ggplot(senior.ht, aes(y= LA, color=User)) + geom_hline(yintercept = 8) +
  geom_hline(yintercept = 32) +
  geom_boxplot() +ggtitle("Player Launch Angle Window") + theme(plot.title = element_text(hjust = 0.5)) + labs( y = "Launch Angle (deg)")  + scale_y_continuous(limits = c(-40, 60))  +
  theme_wsj(base_size = 7)  + 
theme(axis.title = element_text())
plot(la.sd.pl)

# Group LA Window 85 +


gla.sd.pl <- ggplot(senior.hh, aes(y= LA, color=User)) + geom_boxplot() +ggtitle("Player Launch Angle Window on 85+ EV") +
  geom_hline(yintercept = 8) +
  geom_hline(yintercept = 32) +
  theme(plot.title = element_text(hjust = 0.5)) + labs( y = "Launch Angle (deg)") + scale_y_continuous(limits = c(-40, 60))  + theme_wsj(base_size = 6) +
theme(axis.title = element_text())
plot(gla.sd.pl)
```


```{r, echo=FALSE, out.width="50%", include=FALSE}
#POI

s.ht.poi.df <- senior.ht %>%
  group_by(User) %>% 
  summarise_at(vars(POI.Z), list(mean,sd)) 


s.ht.poi.df <-  s.ht.poi.df  %>%
  mutate(Avg_POI = s.ht.poi.df$fn1) %>%
  mutate(SD_POI = s.ht.poi.df$fn2)


s.ht.poi.df <- select(s.ht.poi.df, -c(fn1, fn2))

s.ht.poi.df

#POI85

s.hh.poi.df <- senior.hh %>%
  group_by(User) %>% 
  summarise_at(vars( POI.Z), list(mean,sd)) 


s.total.poi <-  s.ht.poi.df  %>%
  mutate(Avg_POI_85 = s.hh.poi.df$fn1) %>%
  mutate(SD_POI_85 = s.hh.poi.df$fn2)


```

***

```{r, echo=FALSE, out.width="50%"}


s.total.poi %>% 
  kbl(digits = 1) %>%
  kable_paper("hover")


```

<center> <h3>Point of Contact </h3> </center> 


```{r, echo=FALSE, out.width="50%", warning=FALSE}

gpoc.pl <- ggplot(senior.ht, aes(x= POI.X, y=POI.Z,color=User)) + facet_grid(.~User) + geom_boxplot() + 
    geom_jitter(position=position_jitter(0.1),alpha= 0.5) + ggtitle("Point of Contact Window") +  
  labs( y = "Point of Impact Depth (inches)") + geom_segment(aes(x = -8.5, y = 17, xend = 8.5, yend = 17)) +
  geom_segment(aes(x = -8.5, y = 17, xend = -8.5, yend = 8.5)) + 
  geom_segment(aes(x = 8.5, y = 17, xend = 8.5, yend = 8.5)) +
  geom_segment(aes(x = -8.5, y = 8.5, xend = 0, yend = 0)) + geom_segment(aes(x = 8.5, y = 8.5, xend = 0, yend = 0)) + scale_x_continuous(limits = c(-20, 20)) + scale_y_continuous(limits = c(0, 60))  + theme_wsj(base_size = 8) +  theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_text())
plot(gpoc.pl)




hh.gpoc.pl <- ggplot(senior.hh, aes(x= POI.X, y=POI.Z,color=User)) + facet_grid(.~User) + geom_boxplot() + 
  geom_jitter(position=position_jitter(0.1),alpha= 0.5) + ggtitle("Point of Contact Window")  + labs( y = "Point of Impact Depth (inches)") + geom_segment(aes(x = -8.5, y = 17, xend = 8.5, yend = 17)) +
 geom_segment(aes(x = -8.5, y = 17, xend = -8.5, yend = 8.5)) + 
  geom_segment(aes(x = 8.5, y = 17, xend = 8.5, yend = 8.5)) +
  geom_segment(aes(x = -8.5, y = 8.5, xend = 0, yend = 0)) + geom_segment(aes(x = 8.5, y = 8.5, xend = 0, yend = 0))+ scale_x_continuous(limits = c(-20, 20)) + scale_y_continuous(limits = c(0, 60)) + theme_wsj(base_size = 8) + 
  theme(plot.title = element_text(hjust = 0.5)) +
theme(axis.title = element_text())
plot(hh.gpoc.pl)

```

* Point of contact data is very important to monitor especially when players are in a bat speed training phase. 

* One aspect of point of contact that I currently believe is under analyzed is the standard deviation of POC. I believe that players with a large POC standard deviation have more adjustabillity. Looking at this for well hit balls is also important additional context. 

***

&nbsp;

```{r, echo=FALSE, out.width="50%", include=FALSE}
ht.leader <- senior.ht %>% 
  mutate(OZ_Swing = Velo > 0.1 & Strike.Zone >= 10) %>%
  mutate(Air_Pull  = Horiz..Angle <= -20 & LA >= 15) %>%
  mutate(GB_Pull = Horiz..Angle <= -20 & LA <= 5) %>%
  mutate(SweetSpot_per = LA >= 8 & LA <= 32) %>%
  mutate(Hard_Hit_per = Velo >= 90) %>%
  mutate(Barrels = Velo > 85 & LA >= 8 & LA <= 32) %>% 
  group_by(User) %>% summarise_at( vars(OZ_Swing, Air_Pull, GB_Pull, SweetSpot_per, Hard_Hit_per, Barrels), list(mean),na.rm=TRUE)



df.ht.leader <- as.data.frame(ht.leader)

print(df.ht.leader, digits = 1)

Sc.table <- df.ht.leader %>% 
  kbl() %>%
  kable_paper("hover")



library(scales)

per.df.leader <- df.ht.leader %>%
  mutate(Barrels = scales::percent(df.ht.leader$Barrels, accuracy = 0.1)) %>%
  mutate(OZ_Swing = scales::percent(df.ht.leader$OZ_Swing, accuracy = 0.1)) %>%
  mutate(Air_Pull = scales::percent(df.ht.leader$Air_Pull, accuracy = 0.1)) %>%
  mutate(GB_Pull = scales::percent(df.ht.leader$GB_Pull, accuracy = 0.1)) %>%
  mutate(SweetSpot_per = scales::percent(df.ht.leader$SweetSpot_per, accuracy = 0.1)) %>%
  mutate(Hard_Hit_per = scales::percent(df.ht.leader$Hard_Hit_per, accuracy = 0.1)) 
```
  
<center> <h3>Statcast Metrics </h3> </center> 



```{r, echo=FALSE, out.width="50%"}

 per.df.leader %>% 
  kbl() %>%
  kable_paper("hover")


```


* These stats should not necessarily be compared apples to apples to the same in-game metrics of the same name. However, being able to hold the training environment constant, these metrics provide a good benchmark for training and improvements that should translate on field.

&nbsp;

***

&nbsp;

```{r LAxEV.g, echo=FALSE, out.width="50%"}

#LA by EV
LAxEV.g  <- ggplot(senior.ht, aes(Velo, y = LA)) + geom_rect(aes(xmin=85,xmax=Inf, ymin=8,ymax=32),fill= "green", alpha = 0.004) + 
  geom_point(aes(color= Type), alpha= .4) + facet_grid(User~.)  +
  geom_hline(yintercept = 8)  +
  geom_hline(yintercept = 32) + geom_vline(xintercept = 85) + ggtitle("Group Barrel Plots") + 
  theme(plot.title = element_text(hjust = .5)) + labs( x = "Exit Velocity (mph)", y = "Launch Angle (deg)") +  theme_wsj(base_size = 9) + theme(plot.title = element_text(hjust = 0.5))
plot(LAxEV.g)

#solo Plot
LAxEV <- ggplot(player.ht.bip, aes(Velo, y = LA)) + geom_rect(aes(xmin=85,xmax=Inf, ymin=8,ymax=32),fill= "green", alpha = 0.004) + geom_point(aes(color= Type))  + geom_hline(yintercept = 8) + 
  theme(plot.title = element_text(hjust = 0.5)) + geom_hline(yintercept = 32) + geom_vline(xintercept = 85) + ggtitle("Rhett Hendricks Barrel Plots")  + labs( x = "Exit Velocity (mph)", y = "Launch Angle (deg)") + theme_wsj(base_size = 8) + theme(plot.title = element_text(hjust = 0.5)) + theme(axis.title = element_text())
plot(LAxEV)
```

***

# **Blast Motion**

&nbsp;

<center> <h3>Summary Statistics </h3> </center> 



```{r, echo=FALSE, fig.align='center', include=FALSE}
###Blast###

#### MUST INPUT PLAYER NAME######

player.blast  <- filter(r21.blast, n.date >= "2020-10-01" & n.date <= "2020-10-17",
                             Bat.Speed..mph. >= 30, player== "Rhett Hendricks")

senior.blast <- r21.blast %>%
  filter(player %in% c ("Avery Grant","Caden Davis","Rhett Hendricks","Jeremy Rader"))

#Bat Speed Summary Stats
player.bs <- player.blast %>%
  select(Bat.Speed..mph. )


p.bs90 <- quantile(player.bs$Bat.Speed..mph., .9)
p.bs90 <- round(p.bs90, digits = 1)

p.avg.bs <- mean(player.bs$Bat.Speed..mph.)
p.avg.bs <- round(p.avg.bs, digits = 1)

p.med.bs <- median(player.bs$Bat.Speed..mph.)
p.med.bs <- round(p.med.bs, digits = 1)

p.max.bs <- max(player.bs$Bat.Speed..mph.)
p.max.bs <- round(p.max.bs, digits = 1)

#Attack Angle Summary Stats
player.aa <- player.blast %>%
  select(Attack.Angle..deg. )


p.aa.sd <- sd(player.aa$Attack.Angle..deg.)
p.aa.sd <- round(p.aa.sd, digits = 1)

p.avg.aa <- mean(player.aa$Attack.Angle..deg.)
p.avg.aa <- round(p.avg.aa, digits = 1)


p.med.aa <- median(player.aa$Attack.Angle..deg.)
p.med.aa <- round(p.med.aa, digits = 1)

#make a blast table
Average.Bat.Speed <- c(p.avg.bs, 70.2)
Ninetieth.Per.Bat.Speed <- c(p.bs90, 75.1)
Max.Bat.Speed <- c(p.max.bs, "NA")

Average.Attack.Angle <- c(p.avg.aa, 10.5)
Attack.Angle.Standard.Dev. <- c(p.aa.sd, 4.9)

blast.tb.df <- data.frame(Names, Average.Bat.Speed,Ninetieth.Per.Bat.Speed, Max.Bat.Speed, Average.Attack.Angle, Attack.Angle.Standard.Dev.)

blast.tb.df %>%
  kbl() %>%
  kable_classic("hover", full_width = F)

```

```{r, echo=FALSE, fig.align='center'}

#Traditional Blast Tables

blast.normal <- senior.blast %>% 
  mutate(Avg.Bat.Speed = Bat.Speed..mph.) %>%
  mutate(Avg.Attack.Angle  = Attack.Angle..deg.) %>%
  mutate(Avg.Early.Con = Early.Connection..deg.) %>%
  mutate(Avg.Con.at.Impact = Connection.at.Impact..deg.) %>%
  mutate(Avg.Rotational.Accel = Rotational.Acceleration..g.) %>%
  group_by(player) %>% summarise_at( vars(Avg.Bat.Speed,Avg.Attack.Angle,Avg.Early.Con, Avg.Con.at.Impact, Avg.Rotational.Accel), list(mean),na.rm=TRUE)


blast.nomral.df <- as.data.frame(blast.normal)



blast.ttc <- senior.blast %>% 
  mutate(Time_to_Con_sec = Time.to.Contact..sec.) %>%
  group_by(player) %>% summarise_at( vars( Time_to_Con_sec ), list(mean),na.rm=TRUE)




ttc.df.blast.leader <- as.data.frame(blast.ttc, digits= 3)


blast.normal.df2 <- merge(blast.nomral.df, ttc.df.blast.leader, by= "player")

blast.normal.df2  %>% 
  kbl(digits = 1) %>%
  kable_paper("hover")

```








***

<center> <h3>Blast Data Visualizations </h3> </center> 

&nbsp;

```{r, echo=FALSE, fig.align='center'}
con.dist <- ggplot(player.blast,aes( fill=player))
con.dist <- con.dist + geom_density(player.blast, mapping =  aes(x= Early.Connection..deg.,  alpha=0.01)) 
con.dist <- con.dist + geom_density(player.blast, mapping =  aes(x= Connection.at.Impact..deg.,  alpha=0.01)) +
  scale_x_continuous(limits = c(50, 140)) + scale_y_continuous(limits = c(0, .08))  +  
   geom_vline(xintercept = 90.72, size=1) + geom_vline(xintercept = 80.25, size = 1)  + geom_vline(xintercept = 102) + geom_vline(xintercept = 72.25) + ggtitle("Connection Score Distributions") + labs( x = "Connection Scores") +
  theme(plot.title = element_text(hjust = 0.5)) +
     theme_wsj(base_size = 9) +
theme(axis.title = element_text())
plot(con.dist)
```

* The bolded lines are the averages for early connection and connection at impact for affiliate level players. The non-bolded lines are within one standard deviation for each metric.

*Affiliate Data via Driveline Baseball*

&nbsp;

<center> <h3>Saber Blast Metrics </h3> </center> 




```{r, echo=FALSE, fig.align='center'}

### Saber Blast

blast.leader <- senior.blast %>% 
  mutate('Pre Barrels' = Bat.Speed..mph. > 71 & Attack.Angle..deg. >= 4 & Attack.Angle..deg. <= 20) %>%
  mutate('Sweet Angles'  = Attack.Angle..deg. >= 4 & Attack.Angle..deg. <= 20) %>%
  mutate('Plus BatSpeed' = Bat.Speed..mph. > 71 ) %>%

  group_by(player) %>% summarise_at( vars('Pre Barrels', 'Sweet Angles', 'Plus BatSpeed'), list(mean),na.rm=TRUE)




df.blast.leader <- as.data.frame(blast.leader)



per.bl.leader <- df.blast.leader %>%
  mutate('Pre Barrels' = scales::percent(df.blast.leader$'Pre Barrels', accuracy = 0.1)) %>%
  mutate('Sweet Angles' = scales::percent(df.blast.leader$'Sweet Angles', accuracy = 0.1)) %>%
  mutate('Plus BatSpeed' = scales::percent(df.blast.leader$'Plus BatSpeed', accuracy = 0.1))
  
  
  
per.df.blast.leader <- as.data.frame(per.bl.leader)




per.df.blast.leader %>% 
  kbl(digits = 3) %>%
  kable_paper("hover")

```

* A Pre-Barrel is a swing that is both above professional average bat speed and within the optimal attack angle range.

* Sweet Angles is a play on Sweet Spot % and is where a swing is within the optimal attack angle range.

* Plus Bat Speed is when a swing is faster than affiliate average.

*Affiliate Data via Driveline Baseball*

&nbsp;


```{R, echo=FALSE, out.width="50%"}
#Pre-Barrel Plots

#group
g.pb <- ggplot(senior.blast, aes(Bat.Speed..mph., y = Attack.Angle..deg.)) + geom_rect(aes(xmin=71,xmax=Inf, ymin=4,ymax=20),fill= "green", alpha = 0.01) + 
  geom_point( alpha= .4) + facet_grid(player~.)  + geom_hline(yintercept = 4) +
  geom_hline(yintercept = 20) + geom_vline(xintercept = 71)  +
  ggtitle("Pre-Barrel Plots")  + labs( x = "Bat Speed (mph)", y = "Attack Angle (deg)")  +
  theme_wsj(base_size = 9)+  theme(axis.title = element_text()) + theme(plot.title = element_text(hjust = 0.5))
plot(g.pb)

# Solo Plots
p.pb <- ggplot(player.blast, aes(Bat.Speed..mph., y = Attack.Angle..deg.)) + geom_rect(aes(xmin=71,xmax=Inf, ymin=4,ymax=20),fill= "green", alpha = 0.01) + 
  geom_point( alpha= .4) + facet_grid(player~.)  + geom_hline(yintercept = 4) +
  geom_hline(yintercept = 20) + geom_vline(xintercept = 71)  +
  ggtitle("Rhett Hendricks Pre-Barrel Plots")  + labs( x = "Bat Speed (mph)", y = "Attack Angle (deg)")  + theme_wsj(base_size = 9) +
theme(axis.title = element_text()) + theme(plot.title = element_text(hjust = 0.5))
plot(p.pb)
```

&nbsp;

```{r, echo=FALSE, out.width="50%"}
#Attack Angle Dist
aa.plot <- ggplot(player.blast, aes(Attack.Angle..deg.,fill=player, color=player)) + geom_density(alpha=0.1) + 
  geom_vline(xintercept = 4) + geom_vline(xintercept = 20) + scale_x_continuous(limits = c(-20, 40)) +
  scale_y_continuous(limits = c(0, .1)) + ggtitle("Player Attack Angle Distributions") + theme(plot.title = element_text(hjust = 0.5)) + labs(x = "Attack Angle (deg)") + theme_wsj(base_size = 8) +
theme(axis.title = element_text())
plot(aa.plot)

#compared to group
g.aa.plot <- ggplot(senior.blast, aes(Attack.Angle..deg.,fill=player, color=player))+ facet_grid(player~.) + 
  geom_density(alpha=0.1) + geom_vline(xintercept = 4) + geom_vline(xintercept = 20)  + ggtitle("Group Attack Angle Distributions") + theme(plot.title = element_text(hjust = 0.5)) + labs(x = "Attack Angle (deg)") + theme_wsj(base_size = 9) +theme(axis.title = element_text())

plot(g.aa.plot)
```

* The lines on the chart represent the optimal range for attack angles (4-20 degrees). 

&nbsp;

```{r, echo=FALSE, message=FALSE, include=FALSE}
#Bat Speed Table

ninety <- senior.blast %>%
  group_by(player) %>%
  mutate("90th% Bat Speed" = quantile(Bat.Speed..mph., .9)) %>%
   summarise_at(vars("90th% Bat Speed"), list(mean),na.rm= TRUE)


ninety.df <- as.data.frame(ninety)




av.per.max <- senior.blast %>%
  group_by(player) %>%
  mutate("Avg/Max Bat Speed" = mean(Bat.Speed..mph.)/ max(Bat.Speed..mph.)) %>%
  summarise_at(vars("Avg/Max Bat Speed"), list(mean),na.rm= TRUE)


av.per.max.df <- as.data.frame(av.per.max)



per.apm.df <- av.per.max.df %>%
  mutate("Avg/Max Bat Speed" = scales::percent(av.per.max.df$`Avg/Max Bat Speed`, accuracy = 0.1))

format.data.frame(per.apm.df, digits= 1)



bat.speed <- senior.blast %>%
  group_by(player) %>%
  mutate('Avg Bat Speed' = Bat.Speed..mph.) %>%
  summarise_at(vars('Avg Bat Speed'), list(mean),na.rm= TRUE)

max.bat.speed <- senior.blast %>%
  group_by(player) %>%
  mutate("Max Bat Speed" = Bat.Speed..mph.) %>%
  summarise_at(vars("Max Bat Speed"), list(max),na.rm= TRUE)


bat.speed <- as.data.frame(bat.speed)

max.bat.df <- as.data.frame(max.bat.speed)



bat.speed <- merge(bat.speed, max.bat.df)

bat.speed.df <- merge(bat.speed, per.apm.df)
 
bat.speed.df2 <- merge(bat.speed.df, ninety.df)

```

<center> <h3>Bat Speed Table </h3> </center> 


```{r, echo=FALSE,fig.align='center'}
 bat.speed.df2 %>% 
  kbl(digits = 1) %>%
  kable_paper("hover")

```


```{r, echo=FALSE, out.width="50%"}
#Bat Speed Dist
bs.dist <- ggplot(player.blast, aes(Bat.Speed..mph.,fill=player, color = player)) + geom_density(alpha=0.1) +
  geom_vline(xintercept = 67.53) + geom_vline(xintercept = 70.17) + scale_x_continuous(limits = c(50, 80)) +
  scale_y_continuous(limits = c(0, .2)) + ggtitle("Player Bat Speed Distributions") +  labs(x = "Bat Speed (mph)")  + theme_wsj(base_size = 9) + theme(plot.title = element_text(hjust = 0.5)) +
theme(axis.title = element_text())
plot(bs.dist)

   #Compared to Group
g.bs.dist <- ggplot(senior.blast, aes(Bat.Speed..mph.,fill=player, color = player)) + facet_grid(player~.) + geom_density(alpha=0.1) + geom_vline(xintercept = 67.53) + geom_vline(xintercept = 70.17) + ggtitle("Group Bat Speed Distributions") +  labs(x = "Bat Speed (mph)")  + theme_wsj(base_size = 9) + theme(plot.title = element_text(hjust = 0.5)) +
theme(axis.title = element_text())
plot(g.bs.dist)
```

* The first line represents college average, the second represents the average affiliate bat speed. 

&nbsp;

```{r, echo=FALSE, out.width="50%", message=FALSE}
#Efficency PLot
e.plot <- ggplot(player.blast, aes(x=Peak.Hand.Speed..mph., y=Bat.Speed..mph.)) + geom_point() + geom_smooth(method = "lm") + ggtitle("Efficiinecy Plot") +  theme_wsj(base_size = 9) + theme(plot.title = element_text(hjust = 0.5))  +
theme(axis.title = element_text()) 
plot(e.plot)

#Rotational Efficiency
rot.e.plot <- ggplot(player.blast, aes(Rotational.Acceleration..g., y=Bat.Speed..mph.)) + geom_point() + geom_smooth(method = "lm") + ggtitle("Rotational Efficiency Plot") +  theme_wsj(base_size = 9) + theme(plot.title = element_text(hjust = 0.5))  +
theme(axis.title = element_text())
plot(rot.e.plot)
```

* Efficiency Plot measures how efficiently the hitter turns hand speed into bat speed.

* Rotational Efficiency measures how efficiently the hitter turns rotational acceleration into bat speed. 
